### 2019-02-27 Sections/cryptowars.tex
Some quotes and editing
minor

@@

@@

What would be more useful would be a quantum equivalent of private-key cryptography\index{Private-key!Cryptography}, whereby a short key can be reused over and over again for different messages, meaning that only a short, shared secret-key would need to be established once-off (or at least very infrequently).

@@

Note that the security of the scheme is information-theoretic\index{Information-theoretic!Security}, and does not make any assumptions about computational security\index{Computational!Security}. Thus, this represents a strong form of quantum private-key cryptography, requiring only very short keys compared to message length that may be reused.

>>>>

\famousquote{The only true wisdom is knowing you know nothing.}{Socrates}
\\
\\
\famousquote{Ignorance more frequently begets confidence than does knowledge.}{Charles Darwin}
\\

@@

\famousquote{While I thought that I was learning how to live, I have been learning how to die.}{Leonardo da Vinci}
\\

@@

What would be more useful would be a quantum equivalent of private-key cryptography\index{Private-key!Cryptography}, whereby a short key can be
used to lock a much longer message.
 % reused over and over again for different messages, meaning that only a short, shared secret-key would need to be established once-off (or at least very infrequently).

@@

Note that the security of the scheme is information-theoretic\index{Information-theoretic!Security}, and does not make any assumptions about computational security\index{Computational!Security} (except we require the assumption that Eve has finite quantum memory). Thus, this represents a strong form of quantum private-key cryptography, requiring only very short keys compared to message length that may be reused.
